Aggressive Scheduling for Numerical Programs

### 2012-05-02 report/draft.tex
finished up sp in spiral

\begin{verbatim}
+( ) Go into the background of software pipelining. How is it done?
+( ) How do we do it in SPIRAL?
\end{verbatim}

>>>>

The implementation of software pipelining in SPIRAL was straightforward, and
involved three indexing functions each for the prologue, epilogue and steady
state, which mapped the instructions in a fully unrolled loop to its correct
position in an unrolled and software pipelined loop.

Additionally, by targeting unrolled code we were able to bypass the need to do
register allocation in SPIRAL. By insuring that the number of instructions in the
pipelined loop is less than the number of registers on the system, the
compiler was able to allocate registers with little to no spills.
